\documentclass{article}\usepackage{amsmath}\begin{document}\title{Simplex Solver}\maketitle\begin{flushleft}\textbf{Problem}\end{flushleft}\begin{flushleft}Given the following linear system and objective function, find the optimal solution. pruebaa\end{flushleft}\begin{equation*}\max{ 3x_1 + 5x_2 } \\ \end{equation*}\[\left\{\begin{array}{c} 25x_1 + 50x_2 \leq 80000 \\  1/2x_1 + 1/4x_2 \leq 700 \\  x_1 \leq 1000 \\ \end{array}\right.\]\begin{flushleft}\textbf{Solution}\end{flushleft}\begin{flushleft}Add slack variables to turn all inequalities to equalities.\end{flushleft}\[\left\{\begin{array}{c} 25x_1 + 50x_2 + s_1 = 80000 \\  1/2x_1 + 1/4x_2 + s_2 = 700 \\  x_1 + s_3 = 1000 \\ \end{array}\right.\]\begin{flushleft}Create the initial tableau of the new linear system.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{ccccc|c}x_1 &x_2 &s_1 &s_2 &s_3 &b \\ \hline25 & 50 & 1 & 0 & 0 & 80000 \\1/2 & 1/4 & 0 & 1 & 0 & 700 \\1 & 0 & 0 & 0 & 1 & 1000 \\ \hline-3 & -5 & 0 & 0 & 0 & 0 \\\end{array}\end{bmatrix}\begin{array}{c}\\s_1 \\s_2 \\s_3 \\\\\end{array}\end{equation*}\begin{flushleft}There are negative elements in the bottom row, so the current solution is not optimal. Thus, pivot to improve the current solution. The entering variable is $x_2$ and the departing variable is $s_1$.\end{flushleft}\begin{flushleft}Perform elementary row operations until the pivot element is 1 and all other elements in the entering column are 0.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{ccccc|c}x_1 &x_2 &s_1 &s_2 &s_3 &b \\ \hline1/2 & 1 & 1/50 & 0 & 0 & 1600 \\3/8 & 0 & -1/200 & 1 & 0 & 300 \\1 & 0 & 0 & 0 & 1 & 1000 \\ \hline-1/2 & 0 & 1/10 & 0 & 0 & 8000 \\\end{array}\end{bmatrix}\begin{array}{c}\\x_2 \\s_2 \\s_3 \\\\\end{array}\end{equation*}\begin{flushleft}There are negative elements in the bottom row, so the current solution is not optimal. Thus, pivot to improve the current solution. The entering variable is $x_1$ and the departing variable is $s_2$.\end{flushleft}\begin{flushleft}Perform elementary row operations until the pivot element is 1 and all other elements in the entering column are 0.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{ccccc|c}x_1 &x_2 &s_1 &s_2 &s_3 &b \\ \hline0 & 1 & 2/75 & -4/3 & 0 & 1200 \\1 & 0 & -1/75 & 8/3 & 0 & 800 \\0 & 0 & 1/75 & -8/3 & 1 & 200 \\ \hline0 & 0 & 7/75 & 4/3 & 0 & 8400 \\\end{array}\end{bmatrix}\begin{array}{c}\\x_2 \\x_1 \\s_3 \\\\\end{array}\end{equation*}\begin{flushleft}There are no negative elements in the bottom row, so we know the solution is optimal. Thus, the solution is: \end{flushleft}\begin{equation*}s_1 = 0, s_2 = 0, s_3 = 200, x_1 = 800, x_2 = 1200, z = 8400\end{equation*}\end{document}